Estimating Uncertainty for Tipping Points with Deep Learning

### 2022-05-12 manuscript/manuscript.Rmd
missed a few

```{r}
forecasts |> filter(simulation=="saddle", group == 1, reps == 1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5, data = saddle_sims) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = saddle_obs) +
  facet_wrap(~forecasting_model, scales = "free") +
  #facet_grid(forecasting_model ~ reps, scales = "free") +
  theme_bw() + 
  ggtitle("Saddle-Node bifurcation")
```

```{r}
forecasts |> filter(simulation=="stochastic", group == 1, reps==1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5, data = stochastic_sims) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = stochastic_obs) +
  facet_wrap(~forecasting_model, scales = "free") +
  #facet_grid(forecasting_model ~ reps, scales = "free") +
  theme_bw() + 
  ggtitle("Stochastic transition")
```

>>>>

```{r}
forecasts |> filter(simulation=="saddle", group == 1, reps == 1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5, data = saddle_obs) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = saddle_obs) +
  facet_wrap(~forecasting_model, scales = "free") +
  #facet_grid(forecasting_model ~ reps, scales = "free") +
  theme_bw() + 
  ggtitle("Saddle-Node bifurcation")
```

```{r}
forecasts |> filter(simulation=="stochastic", group == 1, reps==1) |> 
  ggplot(aes(t, col=type, fill=type)) + 
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5) +
  geom_ribbon(aes(ymin = pmax(lower,0), ymax = upper), alpha=0.5, data = stochastic_obs) +
  geom_line(aes(y=mean)) +
  geom_line(aes(y=mean), data = stochastic_obs) +
  facet_wrap(~forecasting_model, scales = "free") +
  #facet_grid(forecasting_model ~ reps, scales = "free") +
  theme_bw() + 
  ggtitle("Stochastic transition")
```
